\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\begin{document}

\begin{center}
    \textbf{\LARGE Roshan Kharke}\\
    \href{mailto:roshan.kharke@gmail.com}{roshan.kharke@gmail.com} \textbullet\ (+91) 8178338540 \textbullet\ \href{https://github.com/roshan2498}{roshan2498} \textbullet\ \href{https://linkedin.com/in/roshan2498}{nikoCodesroshan.kharke@gmail.com}
\end{center}

\section*{Education}
\textbf{B. Tech Computer Science}, Delhi Technological University\\
\emph{2016 – 2020}\\
CGPA - 7.22

\textbf{Kendriya Vidyalaya, J.N.U}\\
\emph{Class XII (2016)} - 89.8\%\\
\emph{Class X (2014)} - 10 CGPA

\section*{Core}
\begin{itemize}
    \item Operating Systems: Familiarity with both Windows and Linux operating systems.
\end{itemize}

\section*{Projects}
\textbf{Ecommerce Platform}
\begin{itemize}
    \item Developed a feature-rich e-commerce application using MERN Stack (MongoDB, Express, React, Node.js).
    \item Integrated PayPal API for secure and efficient payment processing.
    \item Implemented custom authentication middleware for user access control.
\end{itemize}

\textbf{Chat Application}
\begin{itemize}
    \item A real-time chat room application made using Node, Express, and Socket.io.
    \item Sends and shows messages to a recipient instantly without any page refresh.
    \item Supports custom usernames, join and leave messages, and real-time messaging.
\end{itemize}

\textbf{Task Master}
\begin{itemize}
    \item To-do list app using Flask Framework and SQLite Database.
\end{itemize}

\section*{Publications}
\textbf{Cardiovascular Disease Classification Using Different Algorithms}\\
\emph{25.09.2020}\\
A comparative study on cardiovascular disease classification using diverse machine learning algorithms on UCI Cleveland dataset. Evaluated performance metrics, precision, recall, accuracy, etc. Findings contribute valuable insights for improved heart disease detection.

\end{document}
